---
title: "occupationsconvert"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{occupationsconvert}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(occupationsconvert)
```
## Introduction

The `occupationsconvert` package provides tools to convert Census 2010 occupational codes into ISCO08 occupational codes using a pre-defined crosswalk dataset. This vignette demonstrates how to use the main function `census10_to_isco08` and explains its key features. 

## Installation

You can install the development version of `occupationsconvert` from GitHub:

```{r}
## Installation

# Install devtools if not already installed
install.packages("devtools")

# Install occupationsconvert from GitHub
devtools::install_github("trangu05/occupationsconvert")

```
### Quick example

```{r}

## Quick Start
# Example data
df <- data.frame(Census2010 = c(1020, 2025, 2550, 3655, 6940))

# Convert using the main function
result <- census10_to_isco08(df, "Census2010")
print(result)

```

The function works by initially converting Census codes into SOC2010 codes, and then 
use avaiable crosswalk from SOC2010 into ISCO08 from BLS to convert Census codes into ISCO08.

Some Census 2010 codes can be mapped into multiple SOC2010 codes according to the BLS. For these codes,
I create a one-to-one mapping using simliarities in titles. 

Some SOC2010 codes can also be mapped into multiple ISCO08 codes. If the user specifies one_to_one argument to be FALSE, then all mappings will be kept. If the user sets it to be TRUE, title
similarities will be used to choose only one appropriate ISCO08 code. Warnings will be raised. Users must be very careful when setting one_to_one = TRUE. 


